%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentation}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Presenter for <Testing for Event-Driven Microservices Based on Consumer-Driven Contracts and State Models.>} % Role
    {29th Asia-Pacific Software Engineering Conference (APSEC 2022)} % Event
    {Virtual, Japan} % Location
    {Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced the challenge to test an asynchronized system with existing method.}
        \item {Proposed a study for how to effectively test an Event-driven microservice system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Presenter for <Composite Contract Testing Mechanism for Event-Driven Microservices.>} % Role
    {18th Taiwan Conference on Software Engineering (TCSE 2022))} % Event
    {Taipei} % Location
    {Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced a study that test a Event-driven microservice system with contract testing}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Presenter for <Design for Personal Data Authorization System and two-way payment platform>} % Role
    {2021 National Computer Symposium, NCS 2021} % Event
    {TaiChung, Taiwan} % Location
    {Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced a system with personal data authorization and interaction with the finance system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Presenter for <PDAS: A Digital-Signature-Based Authorization Platform for Digital Personal Data.>} % Role
    {2020 International Computer Symposium (ICS 2020)} % Event
    {Tainan, Taiwan} % Location
    {Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced a study that how to ensure a digital authorization is legal and reliable for a digital contract with personal data.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
